Risk Perceptions for Wearable Devices

### 2015-03-06 tex-inputs/intro.tex
incorporate colleagues' comments untp section 3

The goal of this paper is to gain a better sense of users' privacy concerns when interacting with wearable devices, so that future systems can take these concerns into account when designing privacy notifications. To our knowledge, this is the first large-scale study to investigate user security and privacy concerns for wearable devices. We surveyed 1,782 Internet users about their perceptions of wearable devices and contribute the following: %\\[-0.8cm]

>>>>

The goal of this work is to gain a better sense of users' privacy concerns when interacting with wearable devices, so that future systems can take these concerns into account when designing privacy notifications. To our knowledge, this is the first large-scale study to investigate user security and privacy concerns for wearable devices. We surveyed 1,782 Internet users about their perceptions of wearable devices and contribute the following: %\\[-0.8cm]

### 2015-03-06 tex-inputs/methodology.tex
incorporate colleagues' comments untp section 3

\section{Methodology}
To obtain a comprehensive list of possible risks that wearable devices might present in the future, we examined the sensors, capabilities, permissions, and applications of the most popular wearable devices on the market at the time of this study. At the time of this study, August 2014, the most popular wearable devices included the Fitbit fitness tracker, which continuously monitors heartbeat, steps taken, and sleep patterns~\cite{6_fitbit_2014, 7_time_2014}; the Pebble smartwatch, which can take pictures, send texts, show notifications from online, and push notifications to services~\cite{pebble_smartwatch_2014, 9_verge_2014, 10_readwrite_2014}; and Google Glass~\cite{11_wikipedia_2015, 12_turi_2014}. We used these wearable devices, along with other comparable wearable devices on the market, as inspiration to develop a list of security and privacy risks that users might be concerned about.

We designed a survey to gauge how severe our participants consider these risks to be.
Our survey contained two main sections. In one section, we presented participants with several scenarios---something undesirable that might happen with their wearable device---and asked them to rate their level of concern if each scenario were to happen. This was intended to elicit their perception of the severity and impact of the risk.
The format of this section was based on Felt {\it et al.}'s study of user perceptions of security and privacy risks with mobile devices~\cite{Felt}.
In the other section, we asked participants to compare the risks and benefits of wearable technologies to those of better-understood technologies, following the same methodology from Fischhoff {\it et al.}'s seminal study in risk perception~\cite{Fischhoff}.
%Finally, we collected demographic information, which included a privacy concern scale and whether participants owned any wearable devices.

@@

\subsubsection{Additional Questions}
The exit portion of the survey contained demographic questions asking for age, gender, and education. Then, we asked participants if they owned a wearable device so we could control for prior exposure, and included an open-ended question on what would be the most likely risks associated with wearable devices. We ended with the 10-question Internet Users' Information Privacy Concerns (IUIPC) index~\cite{malhotra2004internet}, so we could control for participants' general privacy attitudes.

>>>>

\section{Methodology}
To obtain a comprehensive list of possible risks that wearable devices might present in the future, we examined the sensors, capabilities, permissions, and applications of the most popular wearable devices on the market. At the time of this study, August 2014, the most popular wearable devices included the Fitbit fitness tracker, which continuously monitors heartbeat, steps taken, and sleep patterns~\cite{6_fitbit_2014, 7_time_2014}; the Pebble smartwatch, which can take pictures, send texts, show notifications from online, and push notifications to services~\cite{pebble_smartwatch_2014, 9_verge_2014, 10_readwrite_2014}; and Google Glass~\cite{11_wikipedia_2015, 12_turi_2014}. We used these wearable devices, along with other comparable wearable devices on the market, as inspiration to develop a list of security and privacy risks that users might be concerned about.

We designed a survey to gauge what risks users consider to be relevant.
Our survey contained two main sections. In one section, we presented participants with several scenarios---something undesirable that might happen with their wearable device---and asked them to rate their level of concern if each scenario were to happen. This was intended to elicit their perception of the severity and impact of the risk.
The format of this section was based on Felt {\it et al.}'s study of user perceptions of security and privacy risks with mobile devices~\cite{Felt}. In the other section, we asked participants to compare the risks and benefits of wearable technologies to those of better-understood technologies, following the same methodology from Fischhoff {\it et al.}'s seminal study in risk perception~\cite{Fischhoff}.
%Finally, we collected demographic information, which included a privacy concern scale and whether participants owned any wearable devices.

@@

\subsubsection{Additional Questions}
The exit portion of the survey contained demographic questions asking for age, gender, and education. We also asked participants if they owned a wearable device so we could control for prior exposure, and included an open-ended question on what would be the most likely risks associated with wearable devices. We ended with the 10-question Internet Users' Information Privacy Concerns (IUIPC) index~\cite{malhotra2004internet}, so we could control for participants' general privacy attitudes.
